BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for BPMN Models

### 2024-07-05 main.tex
Add benchmark result

\textbf{First}, we benchmarked how our tool handles \textbf{BPMN models of growing size}.
We generated 500 synthetic BPMN models starting with five elements up to 4000 elements, increasing linearly in size.
The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).
The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.

>>>>

\textbf{First}, we benchmarked how our tool handles \textbf{BPMN models of growing size}.
We generated 500 synthetic BPMN models starting with five elements up to 4000 elements, increasing linearly in size.
The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{images/model-size-benchmark}
	\caption{Analysis runtime for models of increasing size}
	\label{fig:model-size-benchmark}
\end{figure}

\autoref{fig:model-size-benchmark} shows that the BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime observed in \autoref{fig:model-size-benchmark}.
